### 2020-05-31 writeup/proof_main.tex

Now we first give a proof of Theorem \ref{thm_model_shift} based on Lemma \ref{lem_cov_shift}.

@@

{\cor add some remarks about the difficulty in random matrix theory}

>>>>

Now we first give a proof of Theorem \ref{thm_model_shift} based on Lemma \ref{lem_cov_shift} and Lemma \ref{lem_cov_derivative}.

@@

One can see from the above proof that the main error, $\delta$, of Theorem \ref{thm_model_shift} comes from approximating $\delta_{\beta}$ by $\wt\delta_{\beta}$ in \eqref{bounddelta-}. In order to improve this estimate and obtain an exact asymptotic result as for the $\delta_{\vari}$ term, one needs to study the singular value distribution of the following random matrix:
$$(X_1^{\top}X_1)^{-1}X_2^{\top}X_2 +  {v}^2 .$$
In fact, the eigenvalues of $\cal X:=(X_1^{\top}X_1)^{-1}X_2^{\top}X_2$ has been studied in the name of Fisher matrices; see e.g. \cite{Fmatrix}. However, since $\cal X$ is not symmetric, it is known that its singular values are different from the eigenvalues. To the best of our knowledge, the asymptotic singular value behavior of $\cal X$ is still unknown in random matrix theory literature, and the study of the singular values of $\cal X + v^2$ will be even harder. We leave this problem to future study.
